\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage[dvipsnames]{xcolor}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{\accentColor}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-5pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand\accentColor{MidnightBlue}

% Bio-Rad: Software Intern - diagnostics instruments, verification, logs, Python automation

\begin{document}

\begin{center}
  {\Huge \scshape \textcolor{\accentColor}{Issac Roy}} \\ \vspace{1pt}
  U.S. Citizen $|$ Test Engineering Intern $|$ San Diego, CA \\ \vspace{1pt}
  \small \raisebox{-0.1\height}{\href{https://www.issacroy.com}{\raisebox{-0.2\height}\faGlobe\ \underline{issacroy.com}} ~
    \href{https://github.com/TheBoyRoy05}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/TheBoyRoy05}} ~
    \href{https://linkedin.com/in/issacroy/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/issacroy}} ~ \href{mailto:issacroy05@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{issacroy05@gmail.com}} ~ \raisebox{-0.1\height}{\reflectbox{\faPhone}}\ 858-428-4311}
  \vspace{-8pt}
\end{center}

\section{\textcolor{\accentColor}{Education}}
\resumeSubHeadingListStart
\resumeSubheading{University of California San Diego (3.98 GPA)}{March 2027}{\textbf{B.S. Data Science} $|$ Math Minor $|$ Cognitive Science Minor}{San Diego, CA}
\vspace{-5pt}
\small\item\textbf{Courses:} Data Structures, Systems Programming, Computer Organization, Statistics, Database Management
\resumeSubHeadingListEnd
\vspace{-20pt}

\section{\textcolor{\accentColor}{Experience}}
\vspace{-7pt}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{MC Computer Vision Lab at UCSD} $|$ \emph{AI Research Assistant}}{January 2026 -- Present}
\resumeItemListStart
\resumeItem{Engineered an OpenRooms++ automation pipeline on NRP Kubernetes, integrating Trellis2 and Flux 2.0 to transform coarse meshes into high-fidelity 3D assets.}
\resumeItem{Implemented inverse rendering using SAM3D and Laval Indoor HDR to recover PBR texture maps (albedo, roughness) from synthetic imagery for reconstruction experiments.}
\resumeItemListEnd
\vspace{-15pt}

\resumeProjectHeading{\textbf{Neurocrine Biosciences} $|$ \emph{Cloud Engineer Intern}}{June 2025 -- September 2025}
\resumeItemListStart
\resumeItem{Saved \$200k in annual OpEx by architecting and deploying an end-to-end serverless containerized data ingestion pipeline on AWS ECS and Lambda, eliminating dependency on third-party vendors.}
\resumeItem{Saved 50+ hours per month by developing an AI-driven data pipeline with AWS Bedrock, integrating LLM endpoints with AWS Redshift to convert raw patient data into study-specific narratives for study teams.}
\resumeItem{Implemented DevOps workflows using Terraform (IaC), AWS Lambda, and multi-environment CI/CD pipelines; collaborated through Jira and Confluence with documentation for engineering and clinical stakeholders.}
\resumeItemListEnd
\vspace{-15pt}

\resumeProjectHeading{\textbf{San Diego County Taxpayers Association} $|$ \emph{Software Intern}}{October 2024 -- January 2025}
\resumeItemListStart
\resumeItem{Developed a Python data ingestion pipeline with Playwright for dynamic pages, including rate limiting and handling of inconsistent markup.}
\resumeItem{Built a Plotly Dash (React-based) dashboard with client-side caching and tuned callbacks so large tables and charts stayed responsive for policy analysis.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-15pt}

\section{\textcolor{\accentColor}{Projects}}
\vspace{-7pt}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{Project Daedalus} $|$ \emph{C++, Arduino, KiCad, Sensors, Telemetry}}{October 2025 -- Present}
\resumeItemListStart
\resumeItem{Developed flight computer firmware on Arduino-class hardware integrating MPU6050 and BMP388 sensors, LoRa radio telemetry, and high-rate onboard logging for post-flight analysis.}
\resumeItem{Produced custom PCB layouts in KiCad and a protective avionics enclosure in Onshape for additive manufacturing, accounting for shock loading and clearance requirements.}
\resumeItem{Conducted pre-flight system verification and post-flight telemetry review to assess data continuity, dropout rates, and sensor range integrity.}
\resumeItemListEnd
\vspace{-15pt}

\resumeProjectHeading
{\textbf{\href{https://www.issacroy.com/turbo-3d}{\underline{Turbo 3D Engine}}} $|$ \emph{C++, Debugging, Performance}}{March 2025}
\resumeItemListStart
\resumeItem{Implemented a software-only 3D renderer in C++ (rasterization, texture mapping, lighting); isolated defects using incremental test scenes and structured debugging.}
\resumeItem{Stress-tested rendering paths with degenerate geometry and extreme camera parameters to surface numerical instability prior to demonstration milestones.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-15pt}

\section{\textcolor{\accentColor}{Leadership}}
\vspace{-7pt}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{\href{https://www.ds3atucsd.com/}{\underline{Data Science Student Society (DS3)}}} $|$ \emph{Software Lead}}{October 2024 -- Present}
\resumeItemListStart
\resumeItem{Lead a 10-person software team on sprint planning, code review, and releases for the membership portal (1,000+ users).}
\resumeItem{Build production features with React and TypeScript, including Supabase Auth, row-level security in Postgres, and API integration from the client.}
\resumeItem{Maintain GitHub Actions workflows for deploys and pull-request checks.}
\resumeItemListEnd
\vspace{-15pt}
\resumeProjectHeading{\textbf{AWS Cloud Club at UCSD} $|$ \emph{Founder \& VP Technical}}{November 2025 -- Present}
\resumeItemListStart
\resumeItem{Established UCSD's official AWS-affiliated student organization; lead workshops on core services (S3, Lambda, SageMaker), Docker, and Terraform for 200+ members.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-15pt}

\section{\textcolor{\accentColor}{Technical Skills}}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \textbf{Languages: }{Python, C++, SQL, Bash, TypeScript, Java} \\
        \textbf{Hardware \& embedded: }{Arduino, KiCad, IMU and barometer sensors, LoRa, telemetry logging, Onshape, 3D printing} \\
        \textbf{QA: }{Log review, functional regression mindset, defect documentation, Jira, Confluence, pull request review} \\
        \textbf{Automation \& tools: }{Playwright, Plotly Dash, Git, Linux, GitHub Actions, CI/CD, command-line workflows} \\
        \textbf{Cloud: }{AWS (ECS, Lambda), Terraform, Postgres} \\
        \textbf{Certifications: }{AWS Cloud Practitioner, AWS AI Practitioner, AWS Solutions Architect Associate} \\
        \textbf{Productivity: }{Microsoft Word, Excel, PowerPoint; Windows and Linux desktops}
        }}
\end{itemize}
\vspace{-10pt}

\end{document}
