\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage[dvipsnames]{xcolor}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{\accentColor}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-5pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand\accentColor{MidnightBlue}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape \textcolor{\accentColor}{Issac Roy}} \\ \vspace{1pt}
    San Diego, CA \\ \vspace{1pt}
    \small \raisebox{-0.1\height}{\reflectbox{\faPhone}}\ 858-428-4311 ~ \href{mailto:issacroy05@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{issacroy05@gmail.com}} ~ 
    \href{https://linkedin.com/in/issacroy/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/issacroy}}  ~
    \href{https://github.com/TheBoyRoy05}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/TheBoyRoy05}} ~ \href{https://www.issacroy.com}{\raisebox{-0.2\height}\faGlobe\ \underline{issacroy.com}}
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\section{\textcolor{\accentColor}{Education}}
    \resumeSubHeadingListStart
        \resumeSubheading{University of California San Diego (3.98 GPA)}{March 2027}{\textbf{B.S. Data Science} $|$ Math Minor $|$ Cognitive Science Minor}{San Diego, CA}
        % \small{\item{Relevant Coursework: Data Structures & Algorithms, Systems Programming, Computer Architecture, Linear Algebra}} 
        % ^ ADD RELEVANT CS COURSEWORK HERE IF YOU HAVE TAKEN THESE CLASSES
  \resumeSubHeadingListEnd
  \vspace{-15pt}
  
%-----------EXPERIENCE-----------
\section{\textcolor{\accentColor}{Experience}}
\vspace{-7pt}
\resumeSubHeadingListStart
    \resumeProjectHeading{\textbf{Neurocrine Biosciences} $|$ \emph{Software Engineer Intern (Data Infrastructure)}}{June 2025 -- September 2025}
    \resumeItemListStart
        \resumeItem{Architected a serverless, event-driven application on AWS (ECS, Lambda) to automate data ingestion, decoupling system components and reducing operational costs by \$200k annually.}
        \resumeItem{Engineered a production-grade backend pipeline using Python and AWS Bedrock and Redshift, integrating LLM APIs with patient data to generate study-specific narratives to streamline reporting and decision-making for study teams.}
        \resumeItem{Implemented Infrastructure as Code (IaC) using Terraform and built multi-environment CI/CD pipelines, enforcing DevOps best practices and reducing deployment latency.}
    \resumeItemListEnd
    
    \vspace{-15pt}
    \resumeProjectHeading{\textbf{San Diego County Taxpayers Association} $|$ \emph{Data Science Intern}}{October 2024 -- January 2025}
    \resumeItemListStart
        \resumeItem{Developed a robust web scraping service using Playwright (Python) to harvest data from dynamic web pages, engineering solutions for rate-limiting and edge cases.}
        \resumeItem{Developed a high-performance frontend dashboard using Plotly Dash (React-based), implementing client-side caching and callback optimization to render large-scale datasets with sub-second latency to inform policy recommendations.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-15pt}

  %------RELEVANT COURSEWORK-------
  \section{\textcolor{\accentColor}{Relevant Coursework}}
          \begin{multicols}{3}
              \begin{itemize}[itemsep=-5pt, parsep=3pt]
                  \item Advanced Data Structures
                  \item Computer Vision
                  \item Systems Programming
                  \item Database Management
                  \item Computer Organization 
                  \item Artificial Intelligence
              \end{itemize}
          \end{multicols}
    \vspace*{2.0\multicolsep}

%-----------PROJECTS (Systems & Embedded)-----------
\section{\textcolor{\accentColor}{Technical Projects}}
\vspace{-7pt}
\resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{\href{https://github.com/TheBoyRoy05/Turbo-3D/}{\underline{Turbo 3D Engine}}} $|$ \emph{C++, SDL2, Linear Algebra}}{March 2025}
        \resumeItemListStart
            \resumeItem{Built a 3D graphics engine from scratch in C++, implementing a custom rasterization pipeline, matrix transformations for camera space, texture mapping, and lighting without external graphics libraries.}
            \resumeItem{Optimized rendering performance through manual memory management and efficient vertex processing algorithms and a custom linear algebra library.}
        \resumeItemListEnd
    \vspace{-15pt}

    \resumeProjectHeading
        {\textbf{Project Daedalus (Avionics System)} $|$ \emph{C++, Raspberry Pi, OpenRocket}}{October 2025 -- Present}
        \resumeItemListStart
            \resumeItem{Engineering the avionics package for a G-class rocket, programming a Raspberry Pi in C++ to interface with IMU and GPS via I2C for telemetry. Designed a custom 3D-printed fairing to protect electronics under high-G launch loads.}
        \resumeItemListEnd
    \vspace{-15pt}

    \resumeProjectHeading {\textbf{\href{https://www.issacroy.com/\#/yipyap}{\underline{YipYap Chat Application}}} $|$ \emph{React, TypeScript, MongoDB, WebSockets}}{August 2024}
    \resumeItemListStart 
        \resumeItem{Architected a full-stack real-time messaging app using Socket.IO for event-based communication and Express.js for RESTful API endpoints. Implemented JWT authentication and managed a MongoDB database for scalable storage.}
    \resumeItemListEnd 
    \vspace{-15pt}

    \resumeProjectHeading
        {\textbf{Self-Playing Guitar} $|$ \emph{C++, Arduino, Mechatronics}}{December 2023}
        \resumeItemListStart
            \resumeItem{Won 1st place at IEEE's Fall Competition against 30+ teams by engineering a self-playing guitar with custom laser-cut and 3D printed parts, programming a note transcriber in C++ to map musical notes to precise servo motions.}
        \resumeItemListEnd
\resumeSubHeadingListEnd 
\vspace{-15pt}
    
%-----------LEADERSHIP---------------
\section{\textcolor{\accentColor}{Leadership}}
\vspace{-7pt}
\resumeSubHeadingListStart
    \resumeProjectHeading{\textbf{\href{https://www.ds3atucsd.com/}{\underline{Data Science Student Society (DS3)}}} $|$ \emph{Director of Software}}{October 2024 -- Present}
        \resumeItemListStart
            \resumeItem{Directing a team of 10+ engineers to build full-stack web applications for a 1,000+ member community, enforcing Agile workflows and CI/CD standards through Github Actions.}
            \resumeItem{Architected the backend for the centralized membership portal, implementing secure authentication flows and managing complex SQL database schemas on Supabase/Postgres.}
        \resumeItemListEnd
    \vspace{-15pt}
    \resumeProjectHeading
    {\textbf{AWS Cloud Club at UCSD} $|$ \emph{Founder \& VP Technical}}{November 2025 -- Present}
    \resumeItemListStart
        \resumeItem{Established UCSD's official AWS affiliate organization, fostering a technical community focused on upskilling students in cloud computing, serverless architecture, and industry best practices.}
        \resumeItem{Curating and leading technical workshops on core AWS services (S3, Lambda, SageMaker), equipping 200+ members with the practical skills to build and deploy scalable cloud infrastructure.}
    \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-15pt}
  %-----------PROGRAMMING SKILLS-----------
  \section{\textcolor{\accentColor}{Technical Skills}}
   \begin{itemize}[leftmargin=0.15in, label={}]
      \small{\item{
          \textbf{Embedded \& Systems: }{Raspberry Pi, Arduino, I2C, Linux, SDL2} \\ 
          \textbf{Cloud \& DevOps: }{AWS, Terraform, Docker, Git, CI/CD, Postgres, MongoDB, Jira, Confluence}
          }} \\
          \textbf{Languages: }{C++, C, Python, TypeScript, Java, SQL, React, Bash}
   \end{itemize}

\end{document}