\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage[dvipsnames]{xcolor}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{\accentColor}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-5pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand\accentColor{MidnightBlue}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape \textcolor{\accentColor}{Issac Roy}} \\ \vspace{1pt}
    U.S. Citizen, San Diego, CA \\ \vspace{1pt}
    \small \raisebox{-0.1\height}{\href{https://www.issacroy.com}{\raisebox{-0.2\height}\faGlobe\ \underline{issacroy.com}} ~
    \href{https://github.com/TheBoyRoy05}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/TheBoyRoy05}} ~ 
    \href{https://linkedin.com/in/issacroy/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/issacroy}} ~ \href{mailto:issacroy05@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{issacroy05@gmail.com}} ~ \raisebox{-0.1\height}{\reflectbox{\faPhone}}\ 858-428-4311}
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\section{\textcolor{\accentColor}{Education}}
    \resumeSubHeadingListStart
        \resumeSubheading{University of California San Diego (3.98 GPA)}{March 2027}{\textbf{B.S. Data Science} $|$ Math Minor $|$ Cognitive Science Minor}{San Diego, CA}
        \vspace{-5pt}
        \small\item\textbf{Relevant Coursework:} Data Structures, Systems Programming, Database Management Systems, Web Development
  \resumeSubHeadingListEnd
  \vspace{-20pt}
  
%-----------EXPERIENCE-----------
\section{\textcolor{\accentColor}{Experience}}
\vspace{-7pt}
\resumeSubHeadingListStart
    \resumeProjectHeading{\textbf{Neurocrine Biosciences} $|$ \emph{Software Engineer Intern (Data Infrastructure)}}{June 2025 -- September 2025}
    \resumeItemListStart
        \resumeItem{Architected, deployed, and maintained a serverless event-driven microservice on AWS (ECS, Lambda) to automate data ingestion streams, optimizing system throughput and reducing annual OpEx by \$200k.}
        \resumeItem{Built a production-grade backend API using Python and AWS Bedrock, integrating Generative AI endpoints with a Redshift data warehouse to programmatically generate complex study narratives.}
        \resumeItem{Implemented Infrastructure as Code (IaC) using Terraform to deploy multi-environment CI/CD pipelines, reducing deployment latency and enforcing immutable infrastructure patterns.}
    \resumeItemListEnd
    
    \vspace{-15pt}
    \resumeProjectHeading{\textbf{San Diego County Taxpayers Association} $|$ \emph{Technical Intern}}{October 2024 -- January 2025}
    \resumeItemListStart
        \resumeItem{Developed a distributed data ingestion pipeline using Playwright, implementing concurrency controls and proxy rotation to harvest data from dynamic web applications.}
        \resumeItem{Engineered a high-performance dashboard using React-based libraries, implementing client-side caching and callback optimization to render large-scale datasets with sub-second latency.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-15pt}

%-----------PROJECTS (Full Stack)-----------
\section{\textcolor{\accentColor}{Projects}}
\vspace{-7pt}
\resumeSubHeadingListStart

\resumeProjectHeading
        {\textbf{\href{https://www.ds3atucsd.com/}{\underline{DS3 Internal Membership Portal}}} $|$ \emph{React, TypeScript, Supabase, Postgres}}{July 2025 -- Present}
        \resumeItemListStart
            \resumeItem{Architected a centralized membership and admin portals for a 1,000+ member organization, replacing legacy spreadsheet workflows with a secure, responsive web application.}
            \resumeItem{Implemented complex security policies using Row Level Security (RLS) and Role-Based Access Control (RBAC) in Postgres to secure sensitive user data.}
            \resumeItem{Designed a normalized database schema and wrote performant SQL queries to handle member tracking, event attendance, and analytics.}
        \resumeItemListEnd
    \vspace{-15pt}

    \resumeProjectHeading
        {\textbf{\href{https://neuralnector.com}{\underline{Neural Nector}}} $|$ \emph{React, TypeScript, PyTorch, Python, FastAPI, Postgres}}{December 2025}
        \resumeItemListStart
            \resumeItem{Developed a full-stack web application serving 100+ users, featuring a React frontend and a RESTful FastAPI backend deployed on cloud infrastructure to challenge users to distinguish between real and GAN-generated flower images.}
            \resumeItem{Optimized API performance for real-time model inference, managing asynchronous tasks and database transactions to track user game states and leaderboards.}
        \resumeItemListEnd
    \vspace{-15pt}

    \resumeProjectHeading
        {\textbf{OnlyDance} $|$ \emph{React Three Fiber, TypeScript, Python, OpenCV, MediaPipe, FastAPI}}{April 2025}
        \resumeItemListStart
            \resumeItem{Won 1st place at DataHacks 2025 (50+ teams) by building an interactive 3D web app that provides real-time motion feedback using browser-based computer vision with MediaPipe.}
            \resumeItem{Engineered a low-latency feedback loop, processing video frames in the browser and rendering 3D avatars at 60 FPS using React Three Fiber.}
        \resumeItemListEnd
        \vspace{-15pt}

    \resumeProjectHeading {\textbf{\href{https://www.issacroy.com/\#/yipyap}{\underline{YipYap Chat Application}}} $|$ \emph{React, TypeScript, MongoDB, WebSockets}}{August 2024}
    \resumeItemListStart 
        \resumeItem{Architected a real-time messaging application using Socket.IO for bi-directional event-based communication and Express.js for RESTful API endpoints.}
        \resumeItem{Implemented JWT authentication for secure session management and designed a MongoDB schema to efficiently store chat history and user relationships.}
    \resumeItemListEnd 

\resumeSubHeadingListEnd 
\vspace{-15pt}
    
%-----------LEADERSHIP---------------
\section{\textcolor{\accentColor}{Leadership}}
\vspace{-7pt}
\resumeSubHeadingListStart
    \resumeProjectHeading
    {\textbf{AWS Cloud Club at UCSD} $|$ \emph{Founder \& VP Technical}}{November 2025 -- Present}
    \resumeItemListStart
        \resumeItem{Established UCSD's official AWS affiliate organization, leading workshops on Serverless Architecture, Containers, and CI/CD to upskill 200+ students in modern cloud practices.}
    \resumeItemListEnd
    \vspace{-15pt}
    \resumeProjectHeading{\textbf{\href{https://www.ds3atucsd.com/}{\underline{Data Science Student Society (DS3)}}} $|$ \emph{Director of Software}}{October 2024 -- Present}
        \resumeItemListStart
            \resumeItem{Directing a team of 10+ engineers to deliver full-stack web solutions to organizations on campus, reviewing code (PRs) and enforcing Agile workflows (Jira, Sprints) to ensure production-quality releases.}
        \resumeItemListEnd
    
    \resumeSubHeadingListEnd
\vspace{-15pt}
  %-----------PROGRAMMING SKILLS-----------
  \section{\textcolor{\accentColor}{Technical Skills}}
   \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
          \textbf{Languages: }{TypeScript, Python, SQL, C++, Java, Bash} \\
          \textbf{Certifications: }{AWS Cloud Practitioner, AWS AI Practitioner, AWS Solutions Architect Associate} \\
          \textbf{Tools: }{AWS, PostgreSQL, MongoDB, Docker, Terraform, Jira, Confluence, React, Node.js, Express.js, FastAPI} \\
          \textbf{Hobbies: }{3D Printing, Robotics, Guitar, Rubik's Cube (PB: 26.50s), Pool (Tracked every shot for 700+ games)}
   }}
   \end{itemize}
\vspace{-10pt}
\end{document}