\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage[dvipsnames]{xcolor}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{\accentColor}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-5pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand\accentColor{MidnightBlue}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape \textcolor{\accentColor}{Issac Roy}} \\ \vspace{1pt}
    San Diego, CA 92129 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}{\reflectbox{\faPhone}}\ 858-428-4311 ~ \href{mailto:issacroy05@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{issacroy05@gmail.com}} ~ 
    \href{https://linkedin.com/in/issacroy/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/issacroy}}  ~
    \href{https://github.com/TheBoyRoy05}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/TheBoyRoy05}} ~ \href{https://www.issacroy.com}{\raisebox{-0.2\height}\faGlobe\ \underline{issacroy.com}}
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\section{\textcolor{\accentColor}{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California San Diego (4.0 GPA)}{June 2027}
      {\textbf{B.S. Data Science} $|$ Math Minor $|$ Cognitive Science Minor}{San Diego, CA}
  \resumeSubHeadingListEnd
\vspace{-10pt}

%-----------EXPERIENCE-----------
\section{\textcolor{\accentColor}{Experience}}
\vspace{-5pt}
\resumeSubHeadingListStart
\resumeProjectHeading
    {\textbf{Neurocrine Biosciences} $|$ \emph{Data Engineer Intern}}{June 2025 -- Present}
    \resumeItemListStart
        \resumeItem{Architected, developed, and deployed containerized cloud-based web scraper to save \$100k+ in operating expenses.}
        \resumeItem{Operationalized study-specific AI knowledge bases using existing data repository to support study teams.}
        \resumeItem{Deployed scalable data pipelines with AWS serverless functions and Power BI dashboards used by study teams.}
    \resumeItemListEnd
    
\vspace{-15pt}
\resumeProjectHeading
    {\textbf{Data Science Student Society (DS3)} $|$ \emph{Director of Software}}{October 2024 -- Present}
    \resumeItemListStart
        \resumeItem{Leading technical workshops on modern software tools including containerization, cloud fundamentals, web development, and Git, bridging gaps between industry practices and coursework.}
        \resumeItem{Directing the design, development, and deployment of new full-stack websites for UCSD clubs.}
    \resumeItemListEnd
    
\vspace{-15pt}
\resumeProjectHeading
    {\textbf{San Diego Taxpayer's Association} $|$ \emph{Data Science Intern}}{October 2024 -- January 2025}
    \resumeItemListStart
        \resumeItem{Built social media scraper to collect public sentiment data on county policies, contributing to a sentiment analysis tool for taxpayers and policymakers.}
    \resumeItemListEnd
    
\resumeSubHeadingListEnd
\vspace{-15pt}

%-----------PROJECTS-----------
\section{\textcolor{\accentColor}{Projects}}
\resumeSubHeadingListStart
\resumeProjectHeading
    {\textbf{OnlyDance} $|$ \emph{OpenCV, ModelPipe, React, React Three Fiber, TypeScript, Python, FastAPI}}{April 2025}
    \resumeItemListStart
        \resumeItem{Won \textbf{1st place} at DataHacks 2025 against 50+ teams by developing an interactive full-stack app that teaches dance routines using 3D avatars and real-time feedback.}
        \resumeItem{Engineered a real-time similarity scoring system using joint weighting, frame interpolation, and sliding window techniques for robust pose matching.}
    \resumeItemListEnd
\vspace{-15pt}
\resumeProjectHeading
    {\textbf{Predicting Power Outage Severities} $|$ \emph{Python, Scikit-Learn, Pandas, Folium}}{April 2025}
    \resumeItemListStart
        \resumeItem{Created an end-to-end Machine Learning pipeline predicting power outage severities across the U.S. with \textbf{78\% accuracy}.}
        \resumeItem{Performed data cleaning, EDA, hypothesis testing, and feature engineering on temporal and categorical attributes.}
        \resumeItem{Conducted fairness evaluations using permutation tests and bias analysis across states.}
    \resumeItemListEnd
\vspace{-15pt}
\resumeProjectHeading
    {\textbf{YipYap, the Chat App for Yappers} $|$ \emph{React, MongoDB, Express, SocketIO, TypeScript, Figma}}{August 2024}
    \resumeItemListStart
        \resumeItem{Developed and deployed a full-stack chat application enabling real-time communication through SocketIO with a MongoDB and Express.js backend.}
        \resumeItem{Designed user interfaces in Figma, built RESTful APIs, and integrated Minstral AI models for intelligent conversation suggestions, enhancing user engagement.}
        \resumeItem{Expanded skills in backend architecture, database management, authentication, UI/UX design, and large-scale system development and deployment.}
    \resumeItemListEnd
\vspace{-15pt}
\resumeProjectHeading
    {\textbf{Self-Playing Guitar} $|$ \emph{Arduino, CAD, Laser Cutting, 3D Printing}}{December 2023}
    \resumeItemListStart
        \resumeItem{Won \textbf{1st place} against 30+ teams at IEEE's Winter Project Competition with a self playing guitar.}
        \resumeItem{Designed and fabricated custom parts using laser cutting and 3D printing.}
        \resumeItem{Programmed a note transcriber in Arduino C to map musical notes to servo motions.}
    \resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-15pt}

%-----------INVOLVEMENT---------------
\section{\textcolor{\accentColor}{Leadership / Extracurricular}}
    \vspace{-7pt}
    \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{Data Science Student Society (DS3)} $|$ \emph{Director of Software} $|$ \emph{UCSD}}{October 2024 -- Present}
        \resumeItemListStart
            \resumeItem{Introduced Agile methodologies to the organization, improving project management and efficiency.}
            \resumeItem{Lead 10+ students in building software solutions and technical workshops for UCSD organizations.}
        \resumeItemListEnd
        \vspace{-15pt}  
    \resumeProjectHeading
        {\textbf{SANDY Youth Group} $|$ \emph{President} $|$ \emph{San Diego Malayalee Association (SANMA)}}{August 2024 -- Present}
            \resumeItemListStart
                \resumeItem{President of a 30-member youth group, organizing monthly activities and community volunteering efforts.}
                \resumeItem{Collaborated with SANMA leaders to organize cultural events with 500+ attendees.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-15pt}
    
%-----------PROGRAMMING SKILLS-----------
\section{\textcolor{\accentColor}{Technical Skills}}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Certifications: }{AWS Cloud Practitioner, AWS AI Practitioner, AWS Solutions Architect Associate} \\
    \textbf{Proficient: }{Python, SQL, Postgres, React, TypeScript, Linux, Terraform} \\
    \textbf{Experienced: }{PyTorch, Docker, AWS, MongoDB, Java, C, C++, C\#, Go, Lua}
    }}
 \end{itemize}
 \vspace{-8pt}

\end{document}
